---
title: "SONA Analysis"
output: html_notebook
date: 22-02-2021
author: "Siyabonga Africa"
---

This project looks to analyze the State of the Nation Address (SONA) for 2021 by President Cyril Ramaphosa. The PDF document will be scraped and analyzed for trends and patterns with the goal extrapolating the findings to previous SONA speeches.

```{r - packages}
library(pdftools)
library(tidytext)
library(tm)
library(dplyr)
library(tidyr)
library(stringr)
library(tesseract)
library(ggplot2)
library(wordcloud)
library(dendextend)
```

I used this article as the basis of loading PDF documents into RStudio (https://data.library.virginia.edu/reading-pdf-files-into-r-for-text-mining/) 

```{r - data load}
sona_pdf <- pdf_ocr_text(
  'SONA_2021.pdf',
  pages = NULL,
  opw = "",
  upw = "",
  language = "eng",
  dpi = 600
)

typeof(sona_pdf)
```
After scraping the pdf document the next step is to turn it into a corpus using tidytext tools. First I need to convert the character vector into a data frame before turning it into tidy text data set.

```{r - tidytext_corpus}
sona_df <- as_tibble(sona_pdf)
sona_df <- sona_df[2:32,]

sona_df <- str_remove(sona_df, "[VII]")
sona_df <- as_tibble(sona_df)

sona_df <- sona_df %>%
  unnest_tokens(word, value)
```

Next I want to start analyzing the text of the speech. I will start by first counting the frequency of the words. First I need to remove stop words.

```{r word_freq}
sona_df %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

This is a joint exercise where we analyze the SONA speech of president Cyril Ramaphosa, the text miners will be Dumi and Siya, I will do word clouding and dendograms to analyze word frequencies mentioned the most by the President whilst Siya will do topic modelling and probably sentiment analysis to assess which sections in his speech did He(Cyril) mostly emphasize on.
```{r word_count_plot}
sona_counts <- sona_df %>%
  count(word) %>%
  arrange(desc(n))
ggplot(
  sona_counts, aes(x=word, y= n)
) +
  geom_col()

#filter the data
sona_counts2 <- sona_df %>% 
  count(word)%>%
  filter(n > 100) %>%
  arrange(desc(n))

#use co-ord_flip to visualize the data thus far
ggplot(
  sona_counts2, aes(x=word, y=n) 
) +
  geom_col() +
  coord_flip() +
  ggtitle("SONA word counts")

#improve word plot
custom_stop_words <- tribble(
 ~word,  ~lexicon,
 "to",   "CUSTOM",
 "the",  "CUSTOM",
 "of",   "CUSTOM",
 "n",    "CUSTOM",
 "in",   "CUSTOM",
 "and",  "CUSTOM",
 "a",    "CUSTOM",
 "vil",  "CUSTOM",
 "nwe",  "CUSTOM",
 "nto",  "CUSTOM",
 "nthis","CUSTOM",
 "nthe", "CUSTOM",
 "nit",  "CUSTOM",
 "nin",  "CUSTOM",
 "nas",  "CUSTOM",
 "nand", "CUSTOM",
 "south","CUSTOM"
)

stop_words2 <- stop_words %>%
  bind_rows(custom_stop_words)

#removing stop words and visualizing
tidy_sona <- sona_df %>% 
  anti_join(stop_words2) %>%
  count(word, sort = TRUE)

#plot the word plot graph again
sona_count3 <- tidy_sona %>%
  count(word) %>%
  filter (n > 10) %>%
  arrange(desc(n))

#plot
ggplot(sona_count3,
       aes(x=word, y=n)) + 
  geom_col() +
  coord_flip() +
  ggtitle("Review Sona speech")

#word-cloud
word_counts <- tidy_sona %>%
  count(word)

wordcloud(
  words = word_counts$word,
  freq = word_counts$n,
  max.words = 10,
  colors = "blue"
)
  
```




```{r N-grams}
#Perform clustering
sona_dist <- dist(head(tidy_sona))

#convert to hierarchical cluster
sona_hc <- hclust(sona_dist)

#Convert matrix to dendogram
sona_hcd <- as.dendrogram(sona_hc)

#color branches
sona_hcd <- branches_attr_by_labels(sona_hcd, c(1:6), "blue")
  
#plot dendogram
plot(sona_hcd, main = "SONA Speech 2021")




```

