---
title: "SONA ANalysis"
output: html_notebook
date: 22-02-2021
author: "Siyabonga Africa"
---

This project looks to analyze the State of the Nation Address (SONA) for 2021 by President Cyril Ramaphosa. The PDF document will be scraped and analyzed for trends and patterns with the goal extrapolating the findings to previous SONA speeches.

```{r - packages}
library(pdftools)
library(tidytext)
library(tm)
library(dplyr)
library(tidyr)
library(stringr)
```

I used this article as the basis of loading PDF documents into RStudio (https://data.library.virginia.edu/reading-pdf-files-into-r-for-text-mining/) 

```{r - data load}
sona_pdf <- pdf_ocr_text(
  'SONA_2021.pdf',
  pages = NULL,
  opw = "",
  upw = "",
  language = "eng",
  dpi = 600
)

typeof(sona_pdf)
```
After scraping the pdf document the next step is to turn it into a corpus using tidytext tools. First I need to convert the character vector into a data frame before turning it into tidy text data set.

```{r - tidytext_corpus}
sona_df <- as_tibble(sona_pdf)
sona_df <- sona_df[2:32,]

sona_df <- str_remove(sona_df, "[VII]")
sona_df <- as_tibble(sona_df)

sona_df <- sona_df %>%
  unnest_tokens(word, value)
```

Next I want to start analyzing the text of the speech. I will start by first counting the frequency of the words. First I need to remove stop words.

```{r word_freq}
sona_df %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

